2.3: OLS Linear Regression

### 2019-09-24 static/slides/09-slides.Rmd
Fix slides 9 problems

.footnote[<sup>.red[1]</sup> Over `\\((n-1)\\)`, since this is a *sample* statistic.

@@

corrplot(gapminder_cor_table, type="upper", 
         method = "circle", # number for showing correlation coefficient
         order="alphabet", 
         col=brewer.pal(n=8, name="RdBu"))
]

@@

# Tidy OLS in R: broom

@@

# OLS in R IV

@@

```{r, echo=T}
augment(school_reg)
```
]

@@

- `augment()` creates useful new variables in the stored `lm` object
    - `.fitted` are the fitted (predicted) values from the model, i.e. $\hat{Y}_i$
    - `.resid` are the residuals (errors) from the model, i.e. $\hat{u}_i$
]

@@

```{r, echo = T}
# install.packages("equatiomatic") # install for first use
library(equatiomatic)
extract_eq(school_reg, 
           use_coefs = TRUE,
           coef_digits = 2,
           fix_signs = TRUE)
```

@@

```{r, echo = T}
CASchool %>%
  filter(district=="Richmond Elementary") %>%
  dplyr::select(district, testscr, str) # another package masks "select"
```

>>>>

.footnote[<sup>.red[1]</sup> Over `\\(n-1\\)`, since this is a *sample* statistic.

@@

corrplot(gapminder_cor_table, type="upper", 
         method = "circle", # number for showing correlation coefficient
         order="alphabet", 
         col=brewer.pal(n=8, name="RdBu"))
```
]

@@

# Tidy OLS in R: broom I

@@

# Tidy OLS in R: broom II

@@

```{r, echo=T}
# add regression-based values to data
augment(school_reg)
```
]

@@

- `augment()` creates useful new variables in the stored `lm` object
    - `.fitted` are fitted (predicted) values from model, i.e. $\hat{Y}_i$
    - `.resid` are residuals (errors) from model, i.e. $\hat{u}_i$
]

@@

```{r, echo = T}
# install.packages("equatiomatic") # install for first use
library(equatiomatic) # load it
extract_eq(school_reg, # regression lm object
           use_coefs = TRUE, # use names of variables
           coef_digits = 2, # round to 2 digits
           fix_signs = TRUE) # fix negatives (instead of + -)
```

@@

```{r, echo = T}
CASchool %>%
  filter(district=="Richmond Elementary") %>%
  dplyr::select(district, testscr, str)
```
